% ************************** Thesis Abstract *****************************
%Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
  In recent years, lattice-based cryptography has become one of the most
  active research topics in cryptography. Existing security mechanisms are currently evolving
 so as to provide extra usability and
  security features. This research focuses on user authentication issues,
  especially privacy-preserving biometrics authentication. Several known techniques
  use the homomorphic operations of some lattice-based cryptosystems to provide
  privacy-preserving features to the authentication protocol. However, most of
  them still need to rely on a trusted third party to decrypt the authentication
  result. Many protocols assume the so-called "Honest-But-Curious" security model for the
  communicating parties, while the client should rather be assumed to be "malicious" in  authentication scenarios. It is therefore desirable to engineer a solution providing all
  necessary security features while still keeping the protocol working under
  practical performance conditions.
  
  In this thesis, we propose a series of protocols with strong security
  guarantees and reasonable computation time and communication size, suitable for any Hamming Distance-based biometric authentication system. Our
  constructions rely on different state of the art cryptographic techniques
  designed to work with lattice-based cryptosystems.

\end{abstract}
