% ************************** Thesis Abstract *****************************
%Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
  In recent years, lattice-based cryptography has been becoming one of the most
  active research topic in cryptography. Many security mechanisms are adapting
  the technique to improve and provide themselves with extra usability and
  security features, this research focus on user authentication aspect,
  especially privacy preserving biometrics authentication. Many known techniques
  use the homomorphic operations of some lattice-based cryptosystems to provide
  privacy preserving feature to the authentication protocol. However, most of
  them still need to rely on a trusted third party to decrypt the authentication
  result. Many protocols assume Honest-But-Curious security model for the
  communicating parties while the client should be modeled as malicicous in
  authentication scenarios. It is desirable to have a solution that provides all
  of such security features while still keeping the protocol working under
  practical performance.
  
  In this thesis, we construct a series of protocols with strong security
  guarantees and reasonable computation time and communication size, that can be
  applied in any Hamming Distance based biometric authentication system. Our
  constructions rely on different state of the art cryptographic techniques
  designed to work with lattice-based cryptosystems.

\end{abstract}
